Appendix0\_10

### 2018-08-20 paper/Appendices/AppendixD.tex
abstract almost done, proof reading first round done

\NormalTok{CW3idday <-}\StringTok{ }\NormalTok{CW3CB3 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, ID_DAY, CW, CB, MLCJOINT, AGE, SEX)}

\NormalTok{Energy_slots <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"../Energy_slots.csv"}\NormalTok{) }\CommentTok{# change the path accordingly}
\NormalTok{Energy_slots <-}\StringTok{ }\NormalTok{Energy_slots }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{ID =}\NormalTok{ id)}

@@

\NormalTok{Energy_slots <-}\StringTok{ }\NormalTok{Energy_slots }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(CW3idday, }\DataTypeTok{by =} \KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{))}

@@

\NormalTok{FoodbyCB_7slots <-}\StringTok{ }\NormalTok{Energy_slots }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{group_by}\NormalTok{(ID, TimeSlot) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{sumEnergy =} \KeywordTok{sum}\NormalTok{(Tot_Energ),}
            \DataTypeTok{sumCarb =} \KeywordTok{sum}\NormalTok{(Tot_Carb), }
            \DataTypeTok{sumSugar =} \KeywordTok{sum}\NormalTok{(Tot_Sugar), }
            \DataTypeTok{sumStarch =} \KeywordTok{sum}\NormalTok{(Tot_Starch),}
            \DataTypeTok{sumFibre =} \KeywordTok{sum}\NormalTok{(Tot_Fibre), }
            \DataTypeTok{sumNMES =} \KeywordTok{sum}\NormalTok{(Tot_NMES),}
            \DataTypeTok{sumFat =} \KeywordTok{sum}\NormalTok{(Tot_Fat),}
            \DataTypeTok{sumProt =} \KeywordTok{sum}\NormalTok{(Tot_Prot), }
            \DataTypeTok{sumAlc =} \KeywordTok{sum}\NormalTok{(Tot_Alc))}

\CommentTok{# Calculate the sum of each nutrients for each time slots}
\NormalTok{Carbsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumCarb) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumCarb)}

@@

\NormalTok{Energysum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumEnergy) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumEnergy)}
\NormalTok{Energysum[}\KeywordTok{is.na}\NormalTok{(Energysum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{Starchsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumStarch) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumStarch)}
\NormalTok{Starchsum[}\KeywordTok{is.na}\NormalTok{(Starchsum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{Sugarsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumSugar) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumSugar)}
\NormalTok{Sugarsum[}\KeywordTok{is.na}\NormalTok{(Sugarsum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{Fibresum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumFibre) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumFibre)}
\NormalTok{Fibresum[}\KeywordTok{is.na}\NormalTok{(Fibresum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{NMESsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumNMES) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumNMES)}
\NormalTok{NMESsum[}\KeywordTok{is.na}\NormalTok{(NMESsum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{Fatsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumFat) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumFat)}
\NormalTok{Fatsum[}\KeywordTok{is.na}\NormalTok{(Fatsum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{Protsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumProt) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumProt)}
\NormalTok{Protsum[}\KeywordTok{is.na}\NormalTok{(Protsum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{Alcsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumAlc) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumAlc)}
\NormalTok{Alcsum[}\KeywordTok{is.na}\NormalTok{(Alcsum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{NDAYS14 <-}\StringTok{ }\NormalTok{blood14 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Ndays)}

\NormalTok{NDAYS56 <-}\StringTok{ }\NormalTok{blood56 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Ndays)}

\NormalTok{NDAYS78 <-}\StringTok{ }\NormalTok{blood78 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, NDays) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{Ndays =}\NormalTok{ NDays)}

@@

\NormalTok{IntakeSlots <-}\StringTok{ }\NormalTok{Energysum }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Carbsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Sugarsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Starchsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Fibresum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Fatsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Protsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(NMESsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Alcsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(NDAYS, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{)}

@@

\NormalTok{BMI78 <-}\StringTok{ }\NormalTok{blood78 }\OperatorTok{%>%}\StringTok{ }

@@

\NormalTok{         LDL, HDL, Chol, Trig) }\OperatorTok{%>%}\StringTok{ }

@@

         \DataTypeTok{drink =}\NormalTok{ dnoft3) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Years =} \StringTok{"7-8"}\NormalTok{, }\DataTypeTok{MVPAtime =} \OtherTok{NA}\NormalTok{, }\DataTypeTok{MarStat =} \OtherTok{NA}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }

@@

                                 \DataTypeTok{nssec8 =} \OperatorTok{-}\DecValTok{9}\NormalTok{,  }\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{1}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }

@@

                                 \DataTypeTok{ethgrp2 =} \OperatorTok{-}\DecValTok{9}\NormalTok{, }\DataTypeTok{ethgrp5 =} \OperatorTok{-}\DecValTok{9}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }

@@

                                 \DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{8}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }

@@

\NormalTok{         MarStat, LDL, HDL, Chol, Trig) }\OperatorTok{%>%}

@@

         \DataTypeTok{wtb =}\NormalTok{  wtb_CY1234, }\DataTypeTok{drink =}\NormalTok{ dnoft3) }\OperatorTok{%>%}\StringTok{ }

@@

         \DataTypeTok{Years =} \StringTok{"1-4"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }

@@

                                 \DataTypeTok{nssec8 =} \OperatorTok{-}\DecValTok{8}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }

@@

                                 \DataTypeTok{MarSt2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }

@@

                                 \DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }\DataTypeTok{nssec8 =} \DecValTok{99}\NormalTok{)) }\OperatorTok{%>%}\StringTok{ }

@@

\NormalTok{Energy14 <-}\StringTok{ }\NormalTok{food14 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, }
\NormalTok{         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,}
\NormalTok{         Fatg, FatpctotE)}
\NormalTok{Energy14}\OperatorTok{$}\NormalTok{Country[Energy14}\OperatorTok{$}\NormalTok{Country }\OperatorTok{==}\StringTok{ "Northern Ireland"}\NormalTok{] <-}\StringTok{ "NI"}

\NormalTok{Energy56 <-}\StringTok{ }\NormalTok{food56 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Country, Surveyyear, EnergykJ, Carbohydrateg, }
\NormalTok{         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,}
\NormalTok{         Fatg, FatpctotE) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{SurveyYear =}\NormalTok{ Surveyyear)}

\NormalTok{Energy78 <-}\StringTok{ }\NormalTok{food78 }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, }
\NormalTok{         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,}
\NormalTok{         Fatg, FatpctotE)}

@@

\NormalTok{dta_DayofWeek <-}\StringTok{ }\NormalTok{dta_NDNS }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(id, id_dy, DayofWeek)}

@@

\NormalTok{CW3idday <-}\StringTok{   }\NormalTok{CW3idday }\OperatorTok{%>%}\StringTok{  }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(dta_DayofWeek, }\DataTypeTok{by=} \KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"DayNo"}\NormalTok{))}

@@

\CommentTok{# extract only the CB variable (Between individual classes == 1 or 2)}
\NormalTok{CW3CB3_reg <-}\StringTok{ }\NormalTok{CW3CB3_reg }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, AGE, SEX, CB) }

@@

\NormalTok{## dataset for 3by3 multilevel latent classes }
\NormalTok{CW3CB3_regss <-}\StringTok{ }\NormalTok{CW3CB3_reg }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(BMI, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Energy, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }

@@

\NormalTok{weightings <-}\StringTok{ }\NormalTok{CW3CB3_regss }\OperatorTok{%>%}\StringTok{ }\KeywordTok{select}\NormalTok{(ID, wti1to8, wtn1to8, wtb1to8)}

\CommentTok{# Combine the data from nutrient intake at each time slot}
\NormalTok{CW3CB3_7regss <-}\StringTok{ }\NormalTok{CW3CB3_7regss }\OperatorTok{%>%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(IntakeSlots, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{)}

>>>>

\NormalTok{CW3idday <-}\StringTok{ }\NormalTok{CW3CB3 }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, ID_DAY, CW, CB, MLCJOINT, AGE, SEX)}

\NormalTok{Energy_slots <-}\StringTok{ }\KeywordTok{read_csv}\NormalTok{(}\StringTok{"../Energy_slots.csv"}\NormalTok{) }\CommentTok{# change the path accordingly}
\NormalTok{Energy_slots <-}\StringTok{ }\NormalTok{Energy_slots }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{ID =}\NormalTok{ id)}

@@

\NormalTok{Energy_slots <-}\StringTok{ }\NormalTok{Energy_slots }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(CW3idday, }\DataTypeTok{by =} \KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"DayofWeek"}\NormalTok{))}

@@

\NormalTok{FoodbyCB_7slots <-}\StringTok{ }\NormalTok{Energy_slots }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{group_by}\NormalTok{(ID, TimeSlot) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{summarise}\NormalTok{(}\DataTypeTok{sumEnergy =} \KeywordTok{sum}\NormalTok{(Tot_Energ),}
            \DataTypeTok{sumCarb =} \KeywordTok{sum}\NormalTok{(Tot_Carb), }
            \DataTypeTok{sumSugar =} \KeywordTok{sum}\NormalTok{(Tot_Sugar), }
            \DataTypeTok{sumStarch =} \KeywordTok{sum}\NormalTok{(Tot_Starch),}
            \DataTypeTok{sumFibre =} \KeywordTok{sum}\NormalTok{(Tot_Fibre), }
            \DataTypeTok{sumNMES =} \KeywordTok{sum}\NormalTok{(Tot_NMES),}
            \DataTypeTok{sumFat =} \KeywordTok{sum}\NormalTok{(Tot_Fat),}
            \DataTypeTok{sumProt =} \KeywordTok{sum}\NormalTok{(Tot_Prot), }
            \DataTypeTok{sumAlc =} \KeywordTok{sum}\NormalTok{(Tot_Alc))}

\CommentTok{# Calculate the sum of each nutrients for each time slots}
\NormalTok{Carbsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumCarb) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumCarb)}

@@

\NormalTok{Energysum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumEnergy) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumEnergy)}
\NormalTok{Energysum[}\KeywordTok{is.na}\NormalTok{(Energysum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{Starchsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumStarch) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumStarch)}
\NormalTok{Starchsum[}\KeywordTok{is.na}\NormalTok{(Starchsum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{Sugarsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumSugar) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumSugar)}
\NormalTok{Sugarsum[}\KeywordTok{is.na}\NormalTok{(Sugarsum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{Fibresum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumFibre) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumFibre)}
\NormalTok{Fibresum[}\KeywordTok{is.na}\NormalTok{(Fibresum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{NMESsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumNMES) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumNMES)}
\NormalTok{NMESsum[}\KeywordTok{is.na}\NormalTok{(NMESsum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{Fatsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumFat) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumFat)}
\NormalTok{Fatsum[}\KeywordTok{is.na}\NormalTok{(Fatsum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{Protsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumProt) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumProt)}
\NormalTok{Protsum[}\KeywordTok{is.na}\NormalTok{(Protsum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{Alcsum <-}\StringTok{ }\NormalTok{FoodbyCB_7slots }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, TimeSlot, sumAlc) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{spread}\NormalTok{(}\DataTypeTok{key =}\NormalTok{ TimeSlot, }
         \DataTypeTok{value =}\NormalTok{ sumAlc)}
\NormalTok{Alcsum[}\KeywordTok{is.na}\NormalTok{(Alcsum)] <-}\StringTok{ }\DecValTok{0}

@@

\NormalTok{NDAYS14 <-}\StringTok{ }\NormalTok{blood14 }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Ndays)}

\NormalTok{NDAYS56 <-}\StringTok{ }\NormalTok{blood56 }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Ndays)}

\NormalTok{NDAYS78 <-}\StringTok{ }\NormalTok{blood78 }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, NDays) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{Ndays =}\NormalTok{ NDays)}

@@

\NormalTok{IntakeSlots <-}\StringTok{ }\NormalTok{Energysum }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Carbsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Sugarsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Starchsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Fibresum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Fatsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Protsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(NMESsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Alcsum, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(NDAYS, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{)}

@@

\NormalTok{BMI78 <-}\StringTok{ }\NormalTok{blood78 }\OperatorTok{\%>\%}\StringTok{ }

@@

\NormalTok{         LDL, HDL, Chol, Trig) }\OperatorTok{\%>\%}\StringTok{ }

@@

         \DataTypeTok{drink =}\NormalTok{ dnoft3) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{mutate}\NormalTok{(}\DataTypeTok{Years =} \StringTok{"7-8"}\NormalTok{, }\DataTypeTok{MVPAtime =} \OtherTok{NA}\NormalTok{, }\DataTypeTok{MarStat =} \OtherTok{NA}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }

@@

                                 \DataTypeTok{nssec8 =} \OperatorTok{-}\DecValTok{9}\NormalTok{,  }\DataTypeTok{paidemployment =} \OperatorTok{-}\DecValTok{1}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{ }

@@

                                 \DataTypeTok{ethgrp2 =} \OperatorTok{-}\DecValTok{9}\NormalTok{, }\DataTypeTok{ethgrp5 =} \OperatorTok{-}\DecValTok{9}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{ }

@@

                                 \DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{8}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{ }

@@

\NormalTok{         MarStat, LDL, HDL, Chol, Trig) }\OperatorTok{\%>\%}

@@

         \DataTypeTok{wtb =}\NormalTok{  wtb_CY1234, }\DataTypeTok{drink =}\NormalTok{ dnoft3) }\OperatorTok{\%>\%}\StringTok{ }

@@

         \DataTypeTok{Years =} \StringTok{"1-4"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }

@@

                                 \DataTypeTok{nssec8 =} \OperatorTok{-}\DecValTok{8}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{ }

@@

                                 \DataTypeTok{MarSt2 =} \OperatorTok{-}\DecValTok{1}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{ }

@@

                                 \DataTypeTok{cigsta3 =} \OperatorTok{-}\DecValTok{8}\NormalTok{, }\DataTypeTok{nssec8 =} \DecValTok{99}\NormalTok{)) }\OperatorTok{\%>\%}\StringTok{ }

@@

\NormalTok{Energy14 <-}\StringTok{ }\NormalTok{food14 }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, }
\NormalTok{         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,}
\NormalTok{         Fatg, FatpctotE)}
\NormalTok{Energy14}\OperatorTok{$}\NormalTok{Country[Energy14}\OperatorTok{$}\NormalTok{Country }\OperatorTok{==}\StringTok{ "Northern Ireland"}\NormalTok{] <-}\StringTok{ "NI"}

\NormalTok{Energy56 <-}\StringTok{ }\NormalTok{food56 }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Country, Surveyyear, EnergykJ, Carbohydrateg, }
\NormalTok{         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,}
\NormalTok{         Fatg, FatpctotE) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{rename}\NormalTok{(}\DataTypeTok{SurveyYear =}\NormalTok{ Surveyyear)}

\NormalTok{Energy78 <-}\StringTok{ }\NormalTok{food78 }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, Country, SurveyYear, EnergykJ, Carbohydrateg, }
\NormalTok{         CHOpctotE, Proteing, ProteinpctotE, Alcoholg, AlcoholpctotE,}
\NormalTok{         Fatg, FatpctotE)}

@@

\NormalTok{dta_DayofWeek <-}\StringTok{ }\NormalTok{dta_NDNS }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(id, id_dy, DayofWeek)}

@@

\NormalTok{CW3idday <-}\StringTok{   }\NormalTok{CW3idday }\OperatorTok{\%>\%}\StringTok{  }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(dta_DayofWeek, }\DataTypeTok{by=} \KeywordTok{c}\NormalTok{(}\StringTok{"ID"}\NormalTok{, }\StringTok{"DayNo"}\NormalTok{))}

@@

\CommentTok{# extract only the CB variable (Between individual classes == 1 or 2)}
\NormalTok{CW3CB3_reg <-}\StringTok{ }\NormalTok{CW3CB3_reg }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{select}\NormalTok{(ID, AGE, SEX, CB) }

@@

\NormalTok{## dataset for 3by3 multilevel latent classes }
\NormalTok{CW3CB3_regss <-}\StringTok{ }\NormalTok{CW3CB3_reg }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(BMI, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(Energy, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{) }

@@

\NormalTok{weightings <-}\StringTok{ }\NormalTok{CW3CB3_regss }\OperatorTok{\%>\%}\StringTok{ }\KeywordTok{select}\NormalTok{(ID, wti1to8, wtn1to8, wtb1to8)}

\CommentTok{# Combine the data from nutrient intake at each time slot}
\NormalTok{CW3CB3_7regss <-}\StringTok{ }\NormalTok{CW3CB3_7regss }\OperatorTok{\%>\%}\StringTok{ }
\StringTok{  }\KeywordTok{left_join}\NormalTok{(IntakeSlots, }\DataTypeTok{by =} \StringTok{"ID"}\NormalTok{)}
